The `zoon` R package for reproducible and shareable species distribution modelling

### 2016-03-21 ms.Rmd
adding armadillo example

@@

#### Example 1. Modelling the distribution of ???

??? constructed a species distribution model for ??? using ???.

Such a model can be quickly and easily re-constructed as a `zoon` workflow using modules which are already available in the software repository:

```{r, eval=FALSE}
carruthers_et_al <- workflow(
    occurrence = ...,
    covariate = ...,
    process = ...,
    model = ...,
    output = ...)
```

The resulting workflow contains all the code required to re-run the workflow, and the results of executing each module.
`zoon` provides functionality to quickly update an existing workflow object (even one created by someone else) by switching out modules.

@@

```{r, eval=FALSE}
carruthers_et_al_interactive <- ReRunWorkflow(
    carruthers_et_al,
    output = Chain(InteractiveMap, ResponseCurve))
```

@@

<!-- add response curves output here -->

`zoon` users can inspect existing workflows using these and a range of other *output* modules, or create and share their own output modules.

#### Example 2. Evaluating the MaxLike model

>>>>

`zoon` provides functionality to quickly update an existing workflow object (even one created by someone else) by switching out modules.

@@

#### Example 1. Modelling the potential distribution of nine-banded armadillo in the USA

@Feng2015 constructed a MaxEnt species distribution model for nine-banded armadillo in the USA using presence-only data on the species' current distribution, and the bioclim [] set of environmental correlates.
This model was then used to predict areas in the Americas which may be suitable for the species to become established.

Such a model can be quickly and easily re-constructed as a `zoon` workflow using modules available in the ZOON module repository.
@Feng2015 used a combination of occurrence data from GBIF, and additional occurrence data manually collected from the published literature.
Unfortunately the latter data have not been made publically available, so here we use only data from GBIF.
If the the additional data had been made available it would be straightforward to incorporate them, for example using the `LocalOccurrenceData` module.

<!--
covariates Feng & Papes used:
1    annual mean temperature
2    mean diurnal range
3    isothermality
4    temperature seasonality
6    minimum temperature of the coldest month
9    mean temperature of the driest quarter
10   mean temperature of the warmest quarter
12   annual precipitation
15   precipitation seasonality
-->

```{r, eval=FALSE}
Feng_Papes <- workflow(
    occurrence = SpOcc('Dasypus novemcinctus',
                       extent = c(-130, -20, -60, 60)),
    covariate = Bioclim(extent = c(-130, -20, -60, 60),
                        layers = c(1:4, 6, 9, 10, 12, 15)),
    process = Chain(TidyGBIF, # some sort of data cleaning?
                    BufferBackground, # background w/in 2 degrees of occurrences
                    MESSMask),  # mask out areas beyond extremes in train data
    model = MaxEnt,
    output = PrintMap)  # They plotted at 5% omission error level
```

The resulting workflow contains all the code required to re-run the workflow, the input data and the results of executing each module.
The object `Feng_Papes` could therefore be saved as a binary file and shared as a reproducible representation of this research.

@@

```{r, eval=FALSE}
Feng_Papes_interactive <- ReRunWorkflow(
    Feng_Papes,
    output = Chain(PrintMap, InteractiveMap, ResponseCurve))
```

@@

<!-- add the original and the response curves to this figure too -->

#### Example 2. Evaluating MaxLike
